%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[letter,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{geometry} % Added geometry for margin control

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.25in}
% \addtolength{\evensidemargin}{-0.3in}
% \addtolength{\textwidth}{0.5in}
% \addtolength{\topmargin}{-0.55in}
% \addtolength{\textheight}{1in}

% Geometry package for setting uniform margins
\geometry{
  a4paper,
  left=0.5in,   % Set left margin
  right=0.5in,  % Set right margin
  top=0.5in,     % Set top margin
  bottom=0.5in     % Set bottom margin
}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
  % \vspace{-3pt}
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-8pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={--}, leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Pratik Sanjay Bhirud}} 
  & Mobile:~~~+1 (303)-557-8495 
  \\ \href{https://www.linkedin.com/in/pratik-bhirud/}{LinkedIn: https://www.linkedin.com/in/pratik-bhirud/} 
  & Email: \href{mailto:}{pratik.bhirud@colorado.edu} 
  \\ & \href{https://github.com/Pratik0247}{Github: ~~github.com/Pratik0247} \\
\end{tabular*}

%-----------EDUCATION-----------------
\vspace{-10pt}
\section{~~Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {University of Colorado, Boulder}{Colorado, USA}
      {Master of Science - Computer Science; GPA: 4.0}{August 2024 - May 2026}
        % {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Datacenter Scale Computing, Data Mining}}}
      \vspace{-2pt}
    \resumeSubheading
      {BITS Pilani, KK Birla Goa Campus}{Goa, India}
      {Bachelor of Engineering - Computer Science;  GPA: 3.54}{August 2018 - July 2022}
      % {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Object Oriented Programming, Data structures and algorithms, Database systems, Operating Systems, Artificial Intelligence, Information Retrieval, Software Development for Portable Devices}}}
      \vspace{-5pt}
    \resumeSubHeadingListEnd

%-----------Skills Summary-----------------
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~Java, C++, Python, SQL, Bash }
	\resumeSubItem{Frameworks}{~Hive, Calcite, Avatica, JDBC, Spark, Delta Lake, Parquet, Iceberg, REST APIs, Junit, Cucumber, Robot Framework, Py4J, Android, Flask, Docker}
        \resumeSubItem{Tools}{Maven, Gradle, Git, Prometheus, Grafana, YAML, JSON, IntelliJ, Android Studio, PyCharm}
        \resumeSubItem{Databases}{PostgreSQL, MySQL, Redis}
        \resumeSubItem{Cloud and Distributed Computing}{Kubernetes, AWS, Glue, EC2, RDS, GCP, Google Cloud Compute, Google Cloud Storage (GCS), Google Kubernetes Engine (GKE), RabbitMQ, Databricks}
        \resumeSubItem{Operating Systems}{Linux, MacOS, Windows}

\resumeSubHeadingListEnd


%-----------Experience-----------------
\vspace{5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{DataPelago India Pvt Ltd}{Hyderabad, India}
    {Member of Technical Staff}{February 2023 - August 2024}
    \resumeItemListStart
        \resumeItem{Metastore Service Integration}{ Integrated a Hive Metastore service with the query planner, enabling storage and incorporation of table statistics into query planning and simplifying adding new table catalog types.}


        \resumeItem{Metastore API Improvements}{ Designed and built a new Metastore API, optimizing the handling of table statistics, improving code maintainability, and reducing database connection setup time by over \textbf{95\%}.}


        \resumeItem{Metadata cache implementation}{Developed a caching mechanism for the SQL query planner, enforcing repeatable-read isolation and reducing query planning time by over \textbf{50\%}.}

        
        \resumeItem{Support for Delta Lake tables}
        {Engineered robust transaction management for Delta Lake (INSERT, UPDATE, DELETE) and optimized read operations for enhanced performance.}

        
        \resumeItem{ANALYZE command implementation}{Designed and implemented the SQL ANALYZE command to compute table statistics and generate highly efficient execution plans, significantly improving query performance.}
        
        \resumeItem{DataPelago JDBC Driver}{Developed a custom JDBC driver with proprietary features to boost connectivity and provide functionality beyond the open-source offering from Apache Calcite Avatica.}
    \resumeItemListEnd    
    
    \resumeSubheading
		{Dremio Corporation.}{Hyderabad, India (Remote)}
		{Software Engineer}{August 2022 -  February 2023}
    \resumeItemListStart
        \resumeItem{COPY INTO command}
          {Engineered the \texttt{COPY INTO <table>} feature, which \textbf{consolidates a multistep data ingestion pipeline into a single command}, significantly improving user experience and efficiency in importing raw data into Dremio.}
    \resumeItemListEnd

    \vspace{2pt}
    \resumeSubheading
    	{VMWare Inc.}{Bangalore, India}
    	{MTS Intern}{January 2022 - June 2022}
    \resumeItemListStart
        \resumeItem{Test Automation Framework}
          {Designed and prototyped a scalable, intent-driven test automation framework for VMWare's Telco Cloud Automation, to reduce manual testing effort and increase test coverage.}
        \resumeItemWithoutTitle{}{Researched and analyzed technologies like YAML, Py4J, Cucumber, and Robot Framework to find an optimal solution.}
    \resumeItemListEnd


  %   \resumeSubheading
		% {Dremio Corporation}{Hyderabad, India}
		% {SDE Intern}{May 2021 -  August 2021}
  %   \resumeItemListStart
  %       \resumeItem{Delta Lake performance improvement}
  %         {Optimized SQL query performance for Delta Lake tables by leveraging dataset metadata to identify and bypass unnecessary data files, significantly improving query efficiency under filtering conditions.}
  %   \resumeItemListEnd

    
  %   \resumeSubheading
		% {National Informatics Centre}{New Delhi, India}
		% {Summer Intern}{May 2020 - June 2020}
  %   \resumeItemListStart
  %       \resumeItem{Application Security Compliance System}
  %         {Upgraded NIC’s Application Security Compliance System with CentOS 8 support and automated XML report generation, \textbf{reducing audit time from hours to minutes} and improving overall compliance checking efficiency.}
  %   \resumeItemListEnd

\resumeSubHeadingListEnd

% -----------Projects-----------------
% \vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
    \resumeSubheading{NarrateNow}{}{Chapter-wise Audiobook Generation Service}{}
\resumeSubHeadingListEnd
\resumeItemListStart
    \resumeItem{Project Overview}{Built a scalable platform to convert EPUB e-books into chapter-wise audiobooks using containerized microservices, leveraging \textbf{Google Text-To-Speech API}, \textbf{RabbitMQ}, and \textbf{Redis}.}
    \vspace{-5pt}
    \resumeItem{Event-driven}{Designed and implemented an event-driven architecture using \textbf{RabbitMQ} and \textbf{Redis}, enabling asynchronous communication, decoupled microservices, and real-time status tracking across the audiobook generation pipeline.}
    \vspace{-5pt}
    \resumeItem{Cloud Infrastructure Design}{Deployed infrastructure on \textbf{Google Kubernetes Engine (GKE)}, enabling automated scaling and efficient task processing.}
    \vspace{-5pt}
     \resumeItem{User Interface Development}{Built a \textbf{Flask-based web interface} for user uploads, status tracking, and downloading chapter-wise audiobooks.}
     \vspace{-5pt}
    \resumeItem{Storage And File Management}{Integrated \textbf{Google Cloud Storage} for managing intermediate and final audiobook files.}
     \vspace{-5pt}
    \resumeItem{Performance Optimization}{Optimized workflows with parallel processing for reduced latency on large inputs.}
    
\resumeItemListEnd

\resumeSubHeadingListStart
    \resumeSubheading{MoodyTunes}{}{A DL-based Music Mood Classifier}{}
\resumeSubHeadingListEnd
\resumeItemListStart
\resumeItem{Project Overview}{Developed a deep learning-based system to classify songs into emotional moods—happy, sad, calm, and energetic—using enriched datasets and advanced architectures.}
\vspace{-5pt}

\resumeItem{Data Enrichment}{Enhanced a subset of the Spotify 278k dataset by incorporating user-generated tags from Last.fm and audio features extracted from 30-second clips using the Spotify API.}
\vspace{-5pt}

\resumeItem{Model Development}{Implemented and optimized various deep learning architectures, including ANN, RCNN, and LSTM, achieving a peak accuracy of 90.67\%.}
\vspace{-5pt}

\resumeItem{Exploratory Data Analysis}{Performed extensive exploratory data analysis to validate dataset quality and identify mood-specific patterns across audio features such as MFCCs, spectral contrast, and loudness.}
\resumeItemListEnd

%-----------Publications-----------------
% \section{Publications}


% %-----------Responsibilities-----------------
% \vspace{-5pt}
% \section{Responsibilities}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%     {Student Desktop Support Technician}{Boulder, CO, USA}{Office of Information Technology, CU Boulder (Part-time)}{November 2024 - Present}
%     \resumeItemListStart
%         \resumeItemWithoutTitle{}
%           {Supported clients across Linux, macOS, and Windows platforms, resolving hardware and software issues, setting up new computers, ensuring seamless account access, and performing essential repairs to maximize productivity.}
%     \resumeItemListEnd
    
%     \resumeSubheading
%     {Quark Coordinator}{Goa, India}{Department of Photography, BITS Pilani Goa Campus}{April 2020 - July 2021}
%     \resumeItemListStart
%         \resumeItemWithoutTitle{}
%           {Led coordination efforts with fest committees and mentored a team of 60+ juniors, fostering collaboration and ensuring smooth execution of festival activities.}
%     \resumeItemListEnd


% \resumeSubHeadingListEnd

% %-----------Awards-----------------
% \section{Honors and Awards}
% \begin{description}[font=$\bullet$]
% \item {Secured an \textbf{All-India rank of 6 among 95,400} students in the COMEDK Undergraduate Entrance Test 2018}
% \end{description}
% \vspace{-5pt}

\end{document}